---
title: "Tuna otolith FMR "
author: "Clive Trueman"
date: "25/02/2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



``````{r, echo=FALSE, warning=FALSE, fig.height = 7, fig.width = 7, fig.align = "center"}

library(ggplot2)
library(plyr)
library(gridExtra)
library(segmented)
library(tidyverse)
library(patchwork)
library(ggsci)
library(svMisc)
library(ggsci)

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
```


#Suess effect correction for tuna -0.025 per year (Rooker Science)
```{r, echo=FALSE}
SuessCor<- -0.025
```


# different d18Owater values 

```{r, echo=FALSE}
d18Ow<-1 # global average
#first guess water / DIC
d18OwMed <-1.2 #Med - (+/- 0.5?)
d18OwGOM <-1 #GOM - (+/- 0.25?)

```

# different d13C DIC values (gloabl, Med, GOM, unassigned)

```{r, echo=FALSE}
d13C_DIC<-1.5 # global average
d13C_DICMed <- 1 #Med - (+/- 0.5?)
d13C_DICGOM <- 1 #GOM - (+/- 0.5?)
d13C_DIC_Unassign <- 1 #GOM - (+/- 0.5?)
```

## Data load



```{r, echo=FALSE}
setwd("")
data<-read.csv("BFT_FMR.csv", header = TRUE, fill=TRUE)

```

#### supp fig plot (proportion from western origin by year)



summary <- data %>%
 filter(age_group %in% c("post_2yr", "post_2yr_3Mo")) %>%
  filter(caught_EW !="Unknown") %>%
  group_by(yearclass, caught_EW) %>%
  summarize(Gom_Count = sum(Origen == "Gom"),
            Med_Count = sum(Origen == "Med")) %>%
  mutate(TotalCount = Gom_Count + Med_Count,
         Gom_Proportion = Gom_Count / TotalCount,
         Med_Proportion = Med_Count / TotalCount) %>%
  ungroup()
  
  
summary$caught_EW <- factor(summary$caught_EW, levels = c("East", "West", "Unknown", "Central"))  
ggplot(summary, aes(x = yearclass, y = Gom_Proportion, size = Gom_Count, color=caught_EW)) +
    scale_color_npg(breaks = c("East", "West", "Central")) +  # Specify the desired order of categories
  geom_point() +
 
  geom_smooth(method = "lm", se = TRUE, alpha=0.2, lwd=2) +
  guides(size = guide_legend(title = "Number of fish"))+
  theme(axis.text.x = element_text(size = 20)) +
    theme(axis.text.y = element_text(size = 20)) +
  theme(axis.title.x = element_text(size = 24))  +
  theme(axis.title.y = element_text(size = 24)) +
  theme(panel.background = element_rect(fill = "white"))  +
  theme(panel.background = element_rect(colour = "black"))  +
  theme(strip.background = element_rect(fill = "white"))   +
  theme(legend.position = c(0.8, 0.8))+
    theme(
    legend.text = element_text(size = 20),
    legend.title = element_text(size = 24)
  )+
    labs(x = "Year Class", y = "Proportion of Fish Assigned to the Western Population", color = "Capture Origin") 


#Suess correct to latest year in dataset to date (2019 in AZTI dataset)

```{r, echo=FALSE}

yearRef<-2019
data$cor<-yearRef-data$yearclass
data$d13Cs<-(data$cor*SuessCor)+data$d13C

#Suess correct DIC estimates (model year 2019)# correct to 2019 from DIC data not year of capture
# Code allows application of different water d18O to east and west
data['d13C_DIC']<-NA
data$d13C_DIC[data$Origen=="Gom"]<-d13C_DICMed
data$d13C_DIC[data$Origen=="Med"]<-d13C_DICGOM
data$d13C_DIC[data$Origen=="Unassigned"]<-d13C_DIC_Unassign


data['d18Ow']<-NA
data$d18Ow[data$Origen=="Gom"]<-d18OwMed
data$d18Ow[data$Origen=="Med"]<-d18OwGOM
data$d18Ow[data$Origen=="Unassigned"]<-d18Ow



```
#  estimate for diet DIC 

```{r, echo=FALSE}
diet<- -18.5 #(±0.5)


```

 removing data with NA in year class
```{r, echo=FALSE}
data$yearclass<-as.factor(data$yearclass)
data<-data%>%drop_na(yearclass)
```




## set up for MC resampling
```{r, echo=FALSE}

#data<-na.omit(data)


## set up for MC resampling
# estimates of uncertainty
d13C_diet_SD<-0.25 #95% CI range  = 1 per mille
d13Cs_SD<-0.1 #95% CI range  = 0.4 per mille
d13C_DIC_SD<-0.1 #95% CI range  = 0.4 per mille

d18Ow_SD<-0.05 #95% CI range  = 0.2 per mille
d18Ooto_SD<-0.025 #95% CI range  = 0.2 per mille
temp_slope_SD<-0.004#0.04475# estimate, justify, Hoie - 95% range = 0.019
temp_int_SD<-0.03#0.06 = high, 0.03 = low estimate, justify, Hoie  95% range = 0.24


# function for replicate estimates of Cresp + temp
# reps
# output matrix (MC_out)
# individual values of d13Coto, d13C_diet and d13C_DIC and linked uncertainty
# individual values of d18Ooto, d18Ow, slope, intercept and linked uncertainty
# matrix to save rep values into - repeating individual by reps in column
# matrix variables: ID, lifestage, origin, year

  N_inds<-length(data$code)
  count=1
  reps=100

  
 MC_out<-data.frame(matrix(ncol=10,nrow=reps*N_inds, dimnames=list(NULL, c("ID", "Lifestage", "Origin", "Year", "Caught_EW", "Temperature", "Cresp", "Data_owner", "Months_sampled", "Iteration"))))

 

 
  # loop over (rep No) draws with common temp equation slope and intercept for each individual create vectors of [N-inds] lengths with estimates of Cresp and Temp
for (draw in 1:reps){
  progress(draw, progress.bar=TRUE)
  slope<-rnorm(mean=-0.27, sd=temp_slope_SD, 1)
  int<-rnorm(mean=-5.193, sd=temp_int_SD, 1)
  position<-draw*N_inds
  

  
for (ind in 1:N_inds){
  d13C_diet_ct<-rnorm(mean=diet, sd=d13C_diet_SD, 1)
  d13C_DIC_ct<-rnorm(mean=data$d13C_DIC[ind], sd=d13C_DIC_SD, 1)
  d13Cs_ct<-rnorm(mean=data$d13Cs[ind], sd=d13Cs_SD, 1)
  Cresp<-1-((d13C_diet_ct-d13Cs_ct) / (d13C_diet_ct- d13C_DIC_ct))
  iteration<-draw
  d18Ow_ct<-rnorm(mean=data$d18Ow[ind], sd=d18Ow_SD, 1)
  d18Ooto_ct<-rnorm(mean=data$d18O[ind], sd=d18Ooto_SD, 1)
  Temperature<-((d18Ooto_ct- d18Ow_ct)+int)/slope
  
  MC_out$Temperature[(position-N_inds)+ind]<- Temperature
  MC_out$Cresp[(position-N_inds)+ind]<- Cresp
  MC_out$Iteration[(position-N_inds)+ind]<- iteration
   MC_out$ID[(position-N_inds)+ind]<- data$code[ind]
    MC_out$Lifestage[(position-N_inds)+ind]<- data$age_group[ind]
     MC_out$Origin[(position-N_inds)+ind]<- data$Origen[ind]
      MC_out$Year[(position-N_inds)+ind]<- data$year[ind]
      MC_out$Caught_EW[(position-N_inds)+ind]<- data$caught_EW[ind]
      MC_out$Data_owner[(position-N_inds)+ind]<- data$Data_owner[ind]
      MC_out$Months_sampled[(position-N_inds)+ind]<- data$months_sampled[ind]

}
}
  








```


# what is the mean std dev of MC resampled Cresp and temp values?
``````{r, echo=FALSE, warning=FALSE, fig.height = 7, fig.width = 7, fig.align = "center"}
test<-MC_out%>%
    group_by(ID)%>%
    summarise(sd(Cresp), sd(Temperature))
    
MeanStdDevCresp<-mean(test$"sd(Cresp)", na.rm=TRUE)
MeanStdDevTemp<-mean(test$"sd(Temperature)", na.rm=TRUE)
CI_range_Cresp<-4*MeanStdDevCresp
CI_range_Temp<-4*MeanStdDevTemp

CI_range_Cresp
CI_range_Temp
````

``````{r, echo=FALSE, warning=FALSE, fig.height = 7, fig.width = 7, fig.align = "center"}

## Using linear mean equation from Chung et al 2018  Cresp<- 4.01+(0.000971*O2)
MC_out$O2_consumption<-(MC_out$Cresp-0.041)/0.000971
MC_out$Temperature2<-MC_out$Temperature^2

neworder <- c("sub_yearling","yearling","post_2yr_3", "post_2yr")
neworder2 <- c("East","West","Central")
MC_out <- arrange(transform(MC_out,
             Lifestage=factor(Lifestage,levels=neworder)),Lifestage) 
             
MC_out <- arrange(transform(MC_out,
             Caught_EW=factor(Caught_EW,levels=neworder2)),Caught_EW) 
 
 

MC_out$iTemp<-as.integer(MC_out$Temperature)
MC_out$Temperature2<-MC_out$Temperature^2

```







## Master Fig 2 output plot: Cresp vs Temperature -all data -split by age
```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}


xlabT <- "Temperature (°C)"
ylabO2 <- "Oxygen consumption (mgO2/Kg/Hr)"

AZTI_All_TempCresp_Caught<- ggplot(MC_out, aes(Temperature, Cresp, color=Caught_EW), show.legend = FALSE)+
  scale_color_npg()+
  geom_point(shape=".", size=0.05, show.legend = FALSE)+


  theme(axis.text.y = element_text(size = 12)) +
  ylim(0.4, 0.7)+
  xlim(22,33)+
  theme(axis.text.x = element_text(size = 16)) +
  theme(axis.title.x = element_text(size = 18))  +
  theme(axis.title.y = element_text(size = 18)) +
  theme(panel.background = element_rect(fill = "white"))  +
  theme(panel.background = element_rect(colour = "black"))  +
  theme(strip.background = element_rect(fill = "white"))   +
  ylab(expression(C[resp]~(Field~Metabolic~Rate))) + 
  labs(x = xlabT)+
  labs(y=(bquote(C[resp])))


#  Same plot but color by origin
AZTI_All_TempCresp_Origin<- ggplot(MC_out, aes(Temperature, Cresp, color=Origin), show.legend = FALSE)+
  scale_color_npg()+
  geom_point(shape=".", size=0.05, show.legend = FALSE)+


  theme(axis.text.y = element_text(size = 12)) +
  ylim(0.4, 0.7)+
  xlim(22,33)+
  theme(axis.text.x = element_text(size = 16)) +
  theme(axis.title.x = element_text(size = 18))  +
  theme(axis.title.y = element_text(size = 18)) +
  theme(panel.background = element_rect(fill = "white"))  +
  theme(panel.background = element_rect(colour = "black"))  +
  theme(strip.background = element_rect(fill = "white"))   +
  ylab(expression(C[resp]~(Field~Metabolic~Rate))) + 
  labs(x = xlabT)+
  labs(y=(bquote(C[resp])))

```







## quadratic and breakpoint analyses
```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}


# extract the quadratic fit coefficients - write as function -  apply over iterations (i.e. recover 100 estimates of vertex / breakpoint) -save vector of breakpoints to plot as density plot.

Quad_Func <- function(z) {


  model <- lm(Cresp ~ Temperature+Temperature2, z) # Linear model
  vtx<- (-coefficients(model)[2])/(2*(coefficients(model)[3])) # extract vertex
return(vtx)
}





quadfit<-lm(Cresp~Temperature+Temperature2, data=MC_out)
vertex<- (-coefficients(quadfit)[2])/(2*(coefficients(quadfit)[3]))


quadfit_subYr<-lm(Cresp[Lifestage=="sub_yearling"]~Temperature[Lifestage=="sub_yearling"]+Temperature[Lifestage=="sub_yearling"], data=MC_out)
vertex_subYr<- (-coefficients(quadfit_subYr)[2])/(2*(coefficients(quadfit_subYr)[3]))

quadfit_Yr<-lm(Cresp[Lifestage=="yearling"]~Temperature[Lifestage=="yearling"]+Temperature2[Lifestage=="yearling"], data=MC_out)
vertex_Yr<- (-coefficients(quadfit_Yr)[2])/(2*(coefficients(quadfit_Yr)[3]))

quadfit_2Yr_3<-lm(Cresp[Lifestage=="post_2yr_3"]~Temperature[Lifestage=="post_2yr_3"]+Temperature2[Lifestage=="post_2yr_3"], data=MC_out)
vertex_2Yr_3<- (-coefficients(quadfit_2Yr_3)[2])/(2*(coefficients(quadfit_2Yr_3)[3]))

quadfit_2Yr<-lm(Cresp[Lifestage=="post_2yr"]~Temperature[Lifestage=="post_2yr"]+Temperature2[Lifestage=="post_2yr"], data=MC_out)
vertex_2Yr<- (-coefficients(quadfit_2Yr)[2])/(2*(coefficients(quadfit_2Yr)[3]))

```





## Change point analyses to explore thermal limitation - using package segmented (https://cran.r-project.org/web/packages/segmented/segmented.pdf) to fit slopes  https://rdrr.io/cran/segmented/man/plot.segmented.html.




#start with a linear model of Cresp vs temp for all data
```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}


data_breakpoint<-MC_out %>%
  filter(Year%in%c(1996:2010, 2012, 2017))

lm1<-lm(Cresp ~ Temperature, data=data_breakpoint) # have to provide estimates for breakpoints.

my.seg <- segmented(lm1, 
                    seg.Z = ~Temperature, 
                    psi = 25)

# display the summary
summary(my.seg)

# plot as ggplot
fit <- numeric(length(data_breakpoint$Temperature)) * NA
fit[complete.cases(rowSums(cbind(data_breakpoint$Cresp, data_breakpoint$Temperature)))] <- broken.line(my.seg)$fit




```


Apply the segmented model to each age group, return the slopes and breakpoints in a table 

```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}



breakpoint_Func <- function(z) {


  model <- lm(Cresp ~ Temperature, z) # Linear model
  seg_mod <- segmented(model, seg.Z = ~Temperature, 
                    control=seg.control(alpha=0.25)) # Segmented model
  breakpoint <- as.matrix(seg_mod$psi[2]) # Extract breakpoint
  coefficients <- as.matrix(seg_mod$coefficients) # Extract coefficients
  dt<-davies.test(model, ~Temperature, k = 10, alternative = c("two.sided", "less", "greater"), 
    type=c("lrt","wald"), values=NULL, dispersion=NULL)
  summary_curve1 <- as.data.frame(rbind(breakpoint, coefficients, dt$p.value)) 
  varnames<-c("breakpoint","intercept", "Seg1_slope", "Seg2_slope", "NULL", "daviesP")
  summary_curve1 <-cbind(varnames, summary_curve1)

return(summary_curve1)
}

```

Breakpoint by age class
```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}

AgeBreak <- ddply(data_breakpoint, .(Lifestage), breakpoint_Func)

AgeBreak_wide<-pivot_wider(AgeBreak, names_from = varnames, values_from = V1) 



 age_N<-data %>%
    group_by(age_group) %>%
    summarize(n_fish = n())
    
    
    ```
    
    what proportion of post 2yr fish have Temp>28?
```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}
# remove data with NA in ageclass
dataMC<-MC_out %>% drop_na(c(Lifestage, Temperature, Origin))

All28<-dataMC %>%
    summarize(n_fish = n(),
              n_gt28 = sum(Temperature > 28),
              p_gt28 = n_gt28 / n_fish)

Prop28<-dataMC %>%
    group_by(Lifestage) %>%
    summarize(n_fish = n(),
              n_gt28 = sum(Temperature > 28),
              p_gt28 = n_gt28 / n_fish)
````

Estimate Cresp inter quartile range and experienced temperature mode

```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}

### range analysis

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}


#population summary all lifestage
sampleDataAll<-MC_out %>%
  group_by(iTemp) %>%
  summarize (
    CrespMin = min(Cresp, na.rm=TRUE),
    CrespMax = max(Cresp, na.rm=TRUE),
    CrespIQR = IQR(Cresp, na.rm=TRUE),
    CrespQ25 = quantile(Cresp, probs=0.25, na.rm=TRUE),
    CrespQ75 = quantile(Cresp, probs=0.75, na.rm=TRUE),
    CrespSd = sd(Cresp, na.rm=TRUE),
    Number = n(),
    CrespMean = mean(Cresp, na.rm=TRUE))

sampleDataAll$diff<-sampleDataAll$CrespMax-sampleDataAll$CrespMin

sampleDataAll%>% print(n = Inf)







#population summary group by lifestage
sampleData<-MC_out %>%
  group_by(Lifestage, iTemp) %>%
  summarize (
    CrespMin = min(Cresp, na.rm=TRUE),
    CrespMax = max(Cresp, na.rm=TRUE),
    CrespIQR = IQR(Cresp, na.rm=TRUE),
    CrespQ25 = quantile(Cresp, probs=0.25, na.rm=TRUE),
    CrespQ75 = quantile(Cresp, probs=0.75, na.rm=TRUE),
    CrespSd = sd(Cresp, na.rm=TRUE),
    Number = n(),
    CrespMean = mean(Cresp, na.rm=TRUE))

sampleData$diff<-sampleData$CrespMax-sampleData$CrespMin

sampleData%>% print(n = Inf)

# remove low number observations to compare IQR
SampleDataN_15<-filter(sampleData, Number > 1500)



# SD over iterations


#population summary all lifestage
sampleDataAll_iterate<-MC_out %>%
  group_by(Iteration, Lifestage, iTemp) %>%
  summarize (
    CrespMin = min(Cresp, na.rm=TRUE),
    CrespMax = max(Cresp, na.rm=TRUE),
    CrespIQR = IQR(Cresp, na.rm=TRUE),
    CrespQ25 = quantile(Cresp, probs=0.25, na.rm=TRUE),
    CrespQ75 = quantile(Cresp, probs=0.75, na.rm=TRUE),
    CrespSd = sd(Cresp, na.rm=TRUE),
    Number = n(),
    CrespMean = mean(Cresp, na.rm=TRUE))

ModeT_SD<-sampleDataAll_iterate %>% group_by(Iteration, Lifestage) %>% 
summarise((iTemp[which.max(Number)]))
sd(unlist(ModeT_SD[3]))

yearling<-ModeT_SD%>%
filter(Lifestage=="yearling")
sd(unlist(yearling[3]))

sub_yearling<-ModeT_SD%>%
filter(Lifestage=="sub_yearling")
sd(unlist(sub_yearling[3]))


post_2yr_3<-ModeT_SD%>%
filter(Lifestage=="post_2yr_3")
sd(unlist(post_2yr_3[3]))

post_2yr<-ModeT_SD%>%
filter(Lifestage=="post_2yr")
sd(unlist(post_2yr[3]))



# SD over iterations


#population summary all lifestage
sampleData_iterate<-MC_out %>%
  group_by(Iteration, Lifestage, iTemp) %>%
  summarize (
    CrespMin = min(Cresp, na.rm=TRUE),
    CrespMax = max(Cresp, na.rm=TRUE),
    CrespIQR = IQR(Cresp, na.rm=TRUE),
    CrespQ25 = quantile(Cresp, probs=0.25, na.rm=TRUE),
    CrespQ75 = quantile(Cresp, probs=0.75, na.rm=TRUE),
    CrespSd = sd(Cresp, na.rm=TRUE),
    Number = n(),
    CrespMean = mean(Cresp, na.rm=TRUE))

CrespIQR_SD<-sampleData_iterate %>% group_by(Iteration, Lifestage) %>% 
summarise((iTemp[which.max(CrespIQR)]))
sd(unlist(CrespIQR[3]))

yearling<-CrespIQR_SD%>%
filter(Lifestage=="yearling")
sd(unlist(yearling[3]))

sub_yearling<-CrespIQR_SD%>%
filter(Lifestage=="sub_yearling")
sd(unlist(sub_yearling[3]))


post_2yr_3<-CrespIQR_SD%>%
filter(Lifestage=="post_2yr_3")
sd(unlist(post_2yr_3[3]))

post_2yr<-CrespIQR_SD%>%
filter(Lifestage=="post_2yr")
sd(unlist(post_2yr[3]))
````


```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}



# extract the CrespIQR and mode Temp values and build into a vector

CrespIQRT<-SampleDataN_15 %>% group_by(Lifestage) %>% summarise(iTemp[which.max(CrespIQR)])
Cresp_IQRT<-c(pull(sampleDataAll%>% summarise(iTemp[which.max(CrespIQR)])),pull(CrespIQRT))


ModeT<-SampleDataN_15 %>% group_by(Lifestage) %>% summarise(iTemp[which.max(Number)])
T_pref.<-c(pull(sampleDataAll%>% summarise(iTemp[which.max(Number)])),pull(ModeT))




####  Create table for outputs




Age_Group<-c("All", "Age 0", "Yearling", "Post 2 year 3 month", "Post 2 year")
N<-c(N_inds, as.numeric(c(age_N[3,2], age_N[4,2], age_N[2,2],age_N[1,2])))
P28<-signif(as.numeric(c(All28[1,3], Prop28[1,4],  Prop28[2,4], Prop28[3,4], Prop28[4,4])), 2)
BreakT<-signif(as.numeric(c(Break_all_data[1,2], AgeBreak_wide[1,2], AgeBreak_wide[2,2], AgeBreak_wide[3,2], AgeBreak_wide[4,2])), 3)
Slope_low<-signif(as.numeric(c(Break_all_data[3,2], AgeBreak_wide[1,4], AgeBreak_wide[2,4], AgeBreak_wide[3,4], AgeBreak_wide[4,4])), 3)
Slope_high<-signif(as.numeric(c(Break_all_data[4,2], AgeBreak_wide[1,5], AgeBreak_wide[2,5], AgeBreak_wide[3,5], AgeBreak_wide[4,5])), 3)
DaviesP<-signif(as.numeric(c(Break_all_data[6,2], AgeBreak_wide[1,7], AgeBreak_wide[2,7], AgeBreak_wide[3,7], AgeBreak_wide[4,7])), 3)
VertexT<-signif(as.numeric(c(vertex, vertex_subYr, vertex_Yr, vertex_2Yr_3, vertex_2Yr)), 2)


#R2<-rep("NA",6)



Table1<-cbind(Age_Group, N, T_pref., Cresp_IQRT, VertexT, BreakT, Slope_low, Slope_high, DaviesP)

kbl(Table1)%>%
  kable_classic_2("striped", full_width = F)
  #column_spec(4, color = spec_color(Table$VertexT[1:5]),
            #  link = "https://haozhu233.github.io/kableExtra/") %>%
  column_spec(5, color = "white",
              background = spec_color(Table$BreakT[1:5], end = 31))

```

  
build the repeat models by iteration
  
Breakpoint by iteration

```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}

breakpoint_Func_Iterate <- function(z) {


  model <- lm(Cresp ~ Temperature, z) # Linear model
  seg_mod <- segmented(model, seg.Z = ~Temperature, 
                    control=seg.control(alpha=0.25)) # Segmented model
  breakpoint <- as.matrix(seg_mod$psi[2]) # Extract breakpoint

return(breakpoint)
}

IterationBreak <- ddply(data_breakpoint, .(Iteration, Lifestage), breakpoint_Func_Iterate)
# extract the std deviation around the vertices for each life stage
IterationBreakSD <- IterationBreak  %>%
#  group_by(Lifestage) %>%
  summarize(Standard_Deviation = sd(unlist(IterationBreak[3])))
IterationBreakSD 




yearlingBP<-IterationBreak%>%
filter(Lifestage=="yearling")
sd(unlist(yearling[3]))

sub_yearling<-IterationBreak%>%
filter(Lifestage=="sub_yearling")
sd(unlist(sub_yearling[3]))


post_2yr_3<-IterationBreak%>%
filter(Lifestage=="post_2yr_3")
sd(unlist(post_2yr_3[3]))

post_2yr<-IterationBreak%>%
filter(Lifestage=="post_2yr")
sd(unlist(post_2yr[3]))





```
  
Vertex by iteration <- bind vertex and breakpoint columns

```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}

IterationVertex <- ddply(MC_out, .(Iteration,Lifestage), Quad_Func)

IterationVertex<-cbind(IterationVertex, IterationBreak[,3])
# extract the std deviation around the vertices for each life stage
IterationVertexSD <- IterationVertex %>%
  #group_by(Lifestage) %>%
  summarize(Standard_Deviation = sd(Temperature))


colnames(IterationVertex)<-c("Iteration", "Lifestage", "QV_Temperature", "BP_Temperature")
```
  




```{r, echo=FALSE, warning=FALSE, fig.height = 5, fig.width = 7, fig.align = "center"}
##MAIN PLOT 2 - can add inset of the MC sampling or Tpref curves if wanted
  
#tiff('/Users/trueman/Desktop/R scripts/OtoMet/Tuna/Fig_2A.tiff',width = 480, height = 480, units = "px", compression="none", res=300)
levels(MC_out$Origin)[match("no result",levels(MC_out$Origin))] <- "Unk"
levels(MC_out$Origin)[match("",levels(MC_out$Origin))] <- "Unk"


Temp_Cresp_SubYear<-AZTI_All_TempCresp_Caught %+% subset(MC_out, Lifestage %in% c("sub_yearling"))+
 # annotation_custom(ggplotGrob(subyear_iteration), xmin = 27.7, xmax = 33.2, 
   #                    ymin = 0.605, ymax = 0.71)+
                         geom_point(data=data[data$age_group=="sub_yearling",], aes(x=Temp, y=Cresp), color="black", size=0.5, show.legend=FALSE)+
                    geom_segment(aes(x = 22.5, y = (as.numeric(AgeBreak_wide[1,3])+(as.numeric(AgeBreak_wide[1,4])*22.5)), xend =as.numeric(AgeBreak_wide[1,2]), yend = (as.numeric(AgeBreak_wide[1,3]) + (as.numeric(AgeBreak_wide[1,4])*as.numeric(AgeBreak_wide[1,2])))), color="#7E6148FF") +
                     geom_segment(aes(x = as.numeric(AgeBreak_wide[1,2]), y = (as.numeric(AgeBreak_wide[1,3])+(as.numeric(AgeBreak_wide[1,4])*as.numeric(AgeBreak_wide[1,2]))), xend = 31, yend =(as.numeric(AgeBreak_wide[1,3])+(as.numeric(AgeBreak_wide[1,4])*as.numeric(AgeBreak_wide[1,2])))+(as.numeric(AgeBreak_wide[1,5])*(31-as.numeric(AgeBreak_wide[1,2])))   ), color="#7E6148FF")+
   stat_smooth(aes(Temperature, Cresp),method = "lm", formula = y ~ x + I(x^2), size = 1, color="black", se=TRUE, show.legend = FALSE) +
  geom_text(x=23, y=0.68, label="A", size=10, color="black")

dev.off()
                                                         

Temp_Cresp_Year<-AZTI_All_TempCresp_Caught %+% subset(MC_out, Lifestage %in% c("yearling"))+
  #   annotation_custom(ggplotGrob(yearling_iteration), xmin = 21.5, xmax = 27, 
   #                    ymin = 0.605, ymax = 0.71)+
    geom_point(data=data[data$age_group=="yearling",], aes(x=Temp, y=Cresp), color="black", size=0.5, show.legend=FALSE)+
                      geom_segment(aes(x = 22.5, y = (as.numeric(AgeBreak_wide[2,3])+(as.numeric(AgeBreak_wide[2,4])*22.5)), xend = as.numeric(AgeBreak_wide[2,2]), yend = (as.numeric(AgeBreak_wide[2,3])+(as.numeric(AgeBreak_wide[2,4])*as.numeric(AgeBreak_wide[2,2])))), color="#7E6148FF")+
                     geom_segment(aes(x = as.numeric(AgeBreak_wide[2,2]), y = (as.numeric(AgeBreak_wide[2,3])+(as.numeric(AgeBreak_wide[2,4])*as.numeric(AgeBreak_wide[2,2]))), xend = 31, yend =(as.numeric(AgeBreak_wide[2,3])+(as.numeric(AgeBreak_wide[2,4])*as.numeric(AgeBreak_wide[2,2])))+(as.numeric(AgeBreak_wide[2,5])*(31-as.numeric(AgeBreak_wide[2,2])))   ), color="#7E6148FF")+
   stat_smooth(aes(Temperature, Cresp),method = "lm", formula = y ~ x + I(x^2), size = 1, color="black", se=TRUE, show.legend = FALSE) +
    geom_text(x=23, y=0.68, label="B", size=10, color="black")




Temp_Cresp_2Year_3Mo<-AZTI_All_TempCresp_Origin %+% subset(MC_out, Lifestage %in% c("post_2yr_3"))+
     # annotation_custom(ggplotGrob(post2Yr_3mo_iteration), xmin = 27.7, xmax = 33.2, 
      #                 ymin = 0.605, ymax = 0.71)+     
                           geom_point(data=data[data$age_group=="post_2yr_3",], aes(x=Temp, y=Cresp), color="black", size=0.5)+
geom_segment(aes(x = 22.5, y = (as.numeric(AgeBreak_wide[3,3])+(as.numeric(AgeBreak_wide[3,4])*22.5)), xend = as.numeric(AgeBreak_wide[3,2]), yend = (as.numeric(AgeBreak_wide[3,3])+(as.numeric(AgeBreak_wide[3,4])*as.numeric(AgeBreak_wide[3,2])))), color="#7E6148FF")+
                     geom_segment(aes(x = as.numeric(AgeBreak_wide[3,2]), y = (as.numeric(AgeBreak_wide[3,3])+(as.numeric(AgeBreak_wide[3,4])*as.numeric(AgeBreak_wide[3,2]))), xend = 31, yend =(as.numeric(AgeBreak_wide[3,3])+(as.numeric(AgeBreak_wide[3,4])*as.numeric(AgeBreak_wide[3,2])))+(as.numeric(AgeBreak_wide[3,5])*(31-as.numeric(AgeBreak_wide[3,2])))   ), color="#7E6148FF")+
   stat_smooth(aes(Temperature, Cresp),method = "lm", formula = y ~ x + I(x^2), size = 1, color="black", se=TRUE) +
    geom_text(x=23, y=0.68, label="C", size=10, color="black")





Temp_Cresp_2Year_12Mo<-AZTI_All_TempCresp_Origin %+% subset(MC_out, Lifestage %in% c("post_2yr"))+
  #     annotation_custom(ggplotGrob(post2Yr_iteration), xmin = 21.5, xmax = 27, 
   #                    ymin = 0.605, ymax = 0.71)+
                             geom_point(data=data[data$age_group=="post_2yr",], aes(x=Temp, y=Cresp), color="black", size=0.5)+
              geom_segment(aes(x = 22.5, y = (as.numeric(AgeBreak_wide[4,3])+(as.numeric(AgeBreak_wide[4,4])*22.5)), xend = as.numeric(AgeBreak_wide[4,2]), yend = (as.numeric(AgeBreak_wide[4,3])+(as.numeric(AgeBreak_wide[4,4])*as.numeric(AgeBreak_wide[4,2])))), color="#7E6148FF")+
                     geom_segment(aes(x = as.numeric(AgeBreak_wide[4,2]), y = (as.numeric(AgeBreak_wide[4,3])+(as.numeric(AgeBreak_wide[4,4])*as.numeric(AgeBreak_wide[4,2]))), xend = 31, yend =(as.numeric(AgeBreak_wide[4,3])+(as.numeric(AgeBreak_wide[4,4])*as.numeric(AgeBreak_wide[4,2])))+(as.numeric(AgeBreak_wide[4,5])*(31-as.numeric(AgeBreak_wide[4,2])))  ), color="#7E6148FF")+
   stat_smooth(aes(Temperature, Cresp),method = "lm", formula = y ~ x + I(x^2), size = 1, color="black", se=TRUE) +
    geom_text(x=23, y=0.68, label="D", size=10, color="black")






(Temp_Cresp_SubYear+Temp_Cresp_Year)/(Temp_Cresp_2Year_3Mo+Temp_Cresp_2Year_12Mo)


#dev.off()

```


